Supplementary Information

### 2021-02-11 doc/manuscript/MEE_manuscript.Rmd
legends

decadal_plot_BCNM_legend = "Figure S58. (Decadal BCNM)"
decadal_plot_HKK_legend = "Figure S59. (Decadal HKK)"
decadal_plot_SCBI_legend = "Figure S60. (Decadal SCBI)"
decadal_plot_LDW_legend = "Figure S61. (Decadal LDW)"
decadal_plot_HF_legend = "Figure S62. (Decadal HF)"
decadal_plot_ZOF_legend = "Figure S63. (Decadal ZOF)"
decadal_plot_NIO_legend = "Figure S64. (Decadal NIO)"
decadal_plot_LT_legend = "Figure S65. (Decadal LT)"
decadal_plot_CB_legend = "Figure S66. (Decadal CB)"
decadal_plot_SC_legend = "Figure S67. (Decadal SC)"

>>>>

decadal_plot_BCNM_legend = "Figure S58. Relationships between $DBH$ and $BAI$ by decade for BCNM."
decadal_plot_HKK_legend = "Figure S59. Relationships between $DBH$ and $BAI$ by decade for HKK."
decadal_plot_SCBI_legend = "Figure S60. Relationships between $DBH$ and $BAI$ by decade for SCBI."
decadal_plot_LDW_legend = "Figure S61. Relationships between $DBH$ and $BAI$ by decade for LDW."
decadal_plot_HF_legend = "Figure S62. Relationships between $DBH$ and $BAI$ by decade for HF."
decadal_plot_ZOF_legend = "Figure S63. Relationships between $DBH$ and $BAI$ by decade for ZOF."
decadal_plot_NIO_legend = "Figure S64. Relationships between $DBH$ and $BAI$ by decade for NIO."
decadal_plot_LT_legend = "Figure S65. Relationships between $DBH$ and $BAI$ by decade for LT."
decadal_plot_CB_legend = "Figure S66. Relationships between $DBH$ and $BAI$ by decade for CB."
decadal_plot_SC_legend = "Figure S67. Relationships between $DBH$ and $BAI$ by decade for SC."
